---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flashr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{flashr}` is to provide a quick way to view decks of flashcards. This package includes existing flashcard decks. The aim is to include decks from [R for Data Science (second edition)](https://r4ds.hadley.nz/index.html) when it is complete.

## Installation

You can install the development version of `{flashr}` like so:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("JeffreyRStevens/flashr")
```

## Example

To view, for example, the flashcard deck on data types:

```{r example, eval = FALSE}
library(flashr)
flashcard(data_type)
```

This randomizes the order of terms and give terms before descriptions. If you would like to present descriptions before terms:

```{r example2, eval = FALSE}
flashcard(data_type, termsfirst = FALSE)
```

## Citation

To cite `{flashr}`, use:

> Stevens, Jeffrey R. (2022). flashr: Creates flashcards of terms and definitions. (version 0.0.0.9000) https://github.com/JeffreyRStevens/flashr

## Contributing to this package

Contributions to `{flashr}` are most welcome! Feel free to check out [open issues](https://github.com/JeffreyRStevens/flashr/issues) for ideas. And [pull requests](https://github.com/JeffreyRStevens/flashr/pulls) are encouraged, but you may want to [raise an issue](https://github.com/JeffreyRStevens/flashr/issues) or [contact the maintainer](mailto:jeffrey.r.stevens@protonmail.com) first.
