---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flashr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/JeffreyRStevens/flashr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/JeffreyRStevens/flashr?branch=main)
<!-- badges: end -->

Learning all of the functions needed to become proficient in R is a substantial undertaking. Flashcards are a great way to learn the syntax of computer languages (Hermans 2021). The goal of `{flashr}` is to provide a quick way to view decks of flashcards. 

`{flashr}` includes existing flashcard decks, including functions and arguments from [R for Data Science (first edition)](https://r4ds.had.co.nz/). The aim is to include decks from [R for Data Science (second edition)](https://r4ds.hadley.nz) when it is complete.

In addition to built in decks, you can easily create your own decks using CSV files. This allows users to customize existing decks or create completely new decks. Also, while geared toward learning R, this package can be used to build decks for anything---not just computer syntax!

## Installation

You can install the development version of `{flashr}` like so:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("JeffreyRStevens/flashr")
```

## Example

To view, for example, the flashcard deck on data types:

```{r eval = FALSE}
library(flashr)
flashcard(deck = data_types)
```

This randomizes the order of terms and give terms before descriptions. If you would like to present descriptions before terms:

```{r eval = FALSE}
flashcard(deck = data_types, termsfirst = FALSE)
```

To build your own deck, simply save a CSV file with a `term` column and a `description` column. You can also include a `package` column if you want the package name included with the term and a `name` column if you want to specify the title of the deck

```{r}
my_deck <- read.csv("data/operators.csv")
head(my_deck)
```

Then simply run the `flashcard()` function on your file or object. Note that you need to use the `file` argument to specify external files and the `deck` argument to specify existing R objects.

```{r eval = FALSE}
flashcard(file = "data/operators.csv")
flashcard(deck = my_deck)
```


## Citation

To cite `{flashr}`, use:

> Stevens, Jeffrey R. (2022). flashr: Creates flashcards of terms and definitions. (version 0.0.0.9000) https://github.com/JeffreyRStevens/flashr

## Contributing to this package

Contributions to `{flashr}` are most welcome! Feel free to check out [open issues](https://github.com/JeffreyRStevens/flashr/issues) for ideas. And [pull requests](https://github.com/JeffreyRStevens/flashr/pulls) are encouraged, but you may want to [raise an issue](https://github.com/JeffreyRStevens/flashr/issues) or [contact the maintainer](mailto:jeffrey.r.stevens@protonmail.com) first.

## References

Hermans, F. (2021). The Programmer’s Brain. Manning. [https://www.manning.com/books/the-programmers-brain](https://www.manning.com/books/the-programmers-brain)

