---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(flashr)
```

Flashcards are a great way to learn information. The repetition of exposure to terms and their descriptions/definitions helps with remembering those relationships (cite). Hermans (2021)^[Hermans, F. (2021). The Programmer’s Brain. Manning. [https://www.manning.com/books/the-programmers-brain](https://www.manning.com/books/the-programmers-brain)] suggests using flashcards for learning programming languages, which inspired the `{flashr}` package. The aim of this package is to create a simple way to use and generate new decks of flashcards for learning R function or anything else you want to learn!

# Usage
`{flashr}` has a number of built-in flashcard decks to help you learn R, and especially the [tidyverse](tidyverse.org/). The workhorse of the package is the `flashcard()` function, which uses [reveal.js](https://revealjs.com/)^[Via the [revealjs](https://github.com/rstudio/revealjs) R package.] to generate an HTML presentation displaying terms and descriptions. For RStudio users, the flashcard presentation will appear in the Viewer pane. In the viewer, you can advance slides with the right arrow key or by clicking on the right arrow in the presentation.

For example, to create a set of flashcards from the built-in `data_types` deck, simply run:
```{r eval = FALSE}
flashcard(deck = data_types)
```
The presentation will start with the title of the deck, then give a blank slide, then present the first term, followed by the description, and a blank slide. The order of terms/descriptions is randomized when the `flashcard()` function is run, so just re-run it to generate a different order.

## Reversing order
By default, terms are presented before descriptions. So when you see a term, you should try to define/describe the term. But it is possible to reverse the order of this and present descriptions first by including the `termfirst = FALSE` argument.
```{r eval = FALSE}
flashcard(deck = data_types, termsfirst = FALSE)
```

## Including package names
Another feature of `flashcard()` is that it can present the name of the package for each function. Often this is useful to distinguish base R function from functions that require other packages. By default, presentations include the package names. However, you can turn this off with `package = FALSE`.

```{r eval = FALSE}
flashcard(deck = data_types, package = FALSE)
```

## Themes
Because `{flashr}` uses reveal.js to create the presentations, it can use the available [reveal.js themes](https://revealjs.com/themes/). By default, `flashcard()` uses the `moon` theme, but if that doesn't suit you, you can change the theme by setting the `theme` argument. At the moment, available themes are `black`, `white`, `league`, `beige`, `sky`, `night`, `serif`, `simple`, `solarized`, `blood`, and `moon`.
```{r eval = FALSE}
flashcard(deck = data_types, theme = "sky")
```

# Available decks
Currently, `{flashr}` includes a few example decks (`data_types`, `vectors`) and decks of function and arguments derived from [R for Data Science (first edition)](https://r4ds.had.co.nz/). 

# Creating your own decks
In addition to built-in decks, you can create your own decks from CSV files. Simply create a CSV file that includes a column labeled `term` and a column labeled `description`. You can also include a `package` column listing package names and a `title` column to give your presentation a title, but these are optional arguments. Here is an example of a CSV file with all of the columns.

```{r}
my_deck <- read.csv("../data/operators.csv")
knitr::kable(my_deck)
```

If you are referring to an external CSV file for your deck, you must use the `file` argument to 

If you create an R object by reading in your CSV fil

## Expanding your flashcards

### Functions and arguments

### Beyond computing
